
\section{System Description}

\subsection{Storage architecture}
MADden is built to work on top of 
both Postgres 9.1 and 

\subsection{In-database statistical methods}
In order to perform text analytics within the database,
packages need to be in place to run at query time.
MADden utilizes statistical functions found in the 
MADlib library \cite{Cohen:2009:MSN:1687553.1687576}, as
a base for text analytics. MADlib provides a 
backbone for the text analytics functionality, including
Naive Bayes Classification, Parallel LDA \cite{Blei:2003:LDA:944919.944937} ,
Association Rule Mining, Sparse Vector operations, etc. 
\subsection{Text Analytics}
The goal then, is to build on top of the existing functionality of MADlib,
to create a more rich environment for text analytics. This requires the 
addition of new functionality be added in the database. This includes
implementing the Viterbi algorithm in native SQL \cite{wang2011hybrid},
part-of-speech tagging, CRF model discovery, Entity Resolution, 
Sentiment analysis, and other moethods.



\subsection{Query Processing}

\subsection{User Interface}
MADden provides a web-based interface for
constructing queries. The interface allows
users to select a vertical market (NFL, Voting, etc.),
and a vareity of query skeletons associated with
each market. The user can fill in the
blank portions of the query, mad libs style, choosing
data classes and instances to build their query. A SQL
representation of their constructed query is presented to them,
as well as results when they execute their query. 
 

\subsection{Text Analysis in DBMS}


In the database we implemente native analysis of textual
data. Queries that require text

We use the MADlib library \cite{Cohen:2009:MSN:1687553.1687576}.

a line about plda 

\subsection{{\system} Implementation}
To realize this query in our system we ...

-- Our statistical models

create these views

Use udfs

create these views..

Add figure of the architecture

-- Info Exxtraction techniques (get this from Morgan)

-- Bayes  for sentiment analysis



