
\section{Related Work}

%There are existing techniques to add text analytics inside of 
%traditional databases \cite{Jain:2009:BQO:1519103.1519108, Li:2011:SDI:2002440.2002459}.
%These system are mostly rule based and do not provide advanced
%statistical methods.

Systems such as Hazy \cite{Koc:2011:IMC:1952376.1952380}, 
WordSeer \cite{muralidharanvisual} and with BayesStore \cite{Wang:2008:BML:1453856.1453896} provide statistical 
methods inside databases but none of them provide a 
comprehensive toolkit of techniques for querying text within a single query.

%Denilson Barbosa stuff ...

Browse Query Language (BQL\footnote{\url{http://senseidb.github.com/sensei/bql.html}}) developed for SensiDB and 
TweeQL \cite{Marcus:2012:PVD:2094114.2094120} are custom SQL
implementations developed especially for text search.
BQL is an SQL-like interface to a distributed database back end that is highly
specialized for text search. Unlike common NoSQL systems, SenseiDB is able to 
perform joins but lacks transactions. 
Creating advanced statistical queries would require serious engineering effort.
TweeQL is an SQL-like interface to the twitter over data stream that supports 
sophisticated UDFs, complex data types,
a query optimizer other basic relational operations.
Unfortunately, the system does not have the same computational power as RDBMS.

SystemT is an information extraction system that provides declarative information
extraction across text documents.
A SIGMOD tutorial gives an in-depth survey of similar systems
\cite{Chiticariu:2010:EIE:1807167.1807339}.
None of the systems mentioned provide a copious library of statistical methods.

