\documentclass{article}

\begin{document}
\begin{enumerate}
\item Names of the group members and UFIDs

%not sure if it's best to put this into the public with our uf-id on it

Morgan Bauer

Christan Grant

Joir-dan Gumbs

\item Title of the project and abstract
\item Final report should include the following topics:
  \begin{enumerate}

  \item  Introduction (1 page)
    \begin{enumerate}
    \item The problem statement and a summary of the main contributions and results of the project.
    \item What is the responsibility of each member of the group?
    \end{enumerate}

  \item Background (1 page)
    \begin{enumerate}\item
      Background information (basic concepts, algorithms, etc.)
    \item Related work
    \item How is this project different from related work
    \end{enumerate}

  \item System Description (4 pages)
    \begin{enumerate}
    \item What is the final system architecture?
    \item What are the system components and statistical methods developed?
    \item What are the final data products?
    \end{enumerate}

  \item Experiments (2 pages)
    \begin{enumerate}
    \item What datasets have been used? What’s the measure of success?
    \item What are the main experimental results? Effectiveness/performance?
    \end{enumerate}

  \item Conclusion (1 page)
    \begin{enumerate}\item What you have learnt through this project? What are the difficulties you have encountered in terms of systems and algorithms in building the system to deliver the data products? What kinds of Data Science tools/systems are needed?
    \end{enumerate}

  \end{enumerate}

\end{enumerate}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
